---
title: "STAT 331 Portfolio"
author: "Elise Donaho"
theme: minty
format:
  html:
    toc: true
embed-resources: true
layout: margin-left
editor: visual
execute: 
  eval: false
  error: true
  echo: true
  warnings: false
---

[**My Grade:**]{.underline} I believe my grade equivalent to course work evidenced below to be an \_A\_.

[**Learning Objective Evidence:**]{.underline} In the code chunks below, provide code from Lab or Challenge assignments where you believe you have demonstrated proficiency with the specified learning target. Be sure to specify **where** the code came from (e.g., Lab 4 Question 2).

## Working with Data

**WD-1: I can import data from a *variety* of formats (e.g., csv, xlsx, txt, etc.).**

-   `csv` Example 1: **Lab 3 Question 2**

```{r}
#| label: wd-1-csv-1

#using the here::here function to easily look for files already put into the working directory

teacher_evals <- read_csv(here::here("Week 3", "teacher_evals.csv"))

```

-   `csv` Example 2: **Lab 2 Question 1**

```{r}
#| label: wd-1-csv-2

surveys <- read_csv(here::here("Week 2", "surveys.csv"))

```

-   `xlsx:`**Check-In 2.3: Loading Data**

```{r}
#| label: wd-1-xlsx

ages <- read_excel(here::here("ages.xlsx"))
```

**WD-2: I can select necessary columns from a dataset.**

-   Example selecting specified columns: **Lab 3 Question 5**

```{r}
#| label: wd-2-ex-1

teacher_evals_clean <- teacher_evals |> 
  rename(sex = gender) |>
  filter(no_participants >= 10) |>
  mutate(
    teacher_id = as.character(teacher_id),
    course_id = as.character(course_id)
    ) |> 
  select(course_id, 
         teacher_id, 
         question_no, 
         no_participants, 
         resp_share, #<- selecting solely these columns
         SET_score_avg, 
         percent_failed_cur, 
         academic_degree, 
         seniority, sex)

```

-   Example removing specified columns: **Lab 3 Question 5 - Modified**

```{r}
#| label: wd-2-ex-2

teacher_evals_clean <- teacher_evals |> 
  rename(sex=gender) |>
  filter(no_participants >= 10) |>
  mutate(
    teacher_id = as.character(teacher_id),
    course_id = as.character(course_id)
    ) |> 
  select(-course_id,
         -teacher_id, #selecting all columns BUT these 3 (removing the 3)
         -question_no)
```

-   Example selecting columns based on logical values (e.g., `starts_with()`, `ends_with()`, `contains()`, `where()`) **Lab 4 Question 7**

```{r}
#| label: wd-2-ex-3

recreate_plot <- ca_childcare |> 
  select(county_name, 
         study_year, 
         starts_with("mc_"), # find columns that have names that start with mc_
         census_region) |>
  pivot_longer(cols = mc_infant:mc_preschool,
             names_to = "age",
             values_to = "price") |> 
  mutate(age = case_when(age == "mc_infant" ~ "Infant",
                         age == "mc_toddler" ~ "Toddler",
                         age == "mc_preschool" ~ "Preschool",
                         TRUE ~ age),
    census_region = fct_reorder2(.f = census_region, .x = study_year, 
                 .y = price, 
                .desc = TRUE))
```

**WD-3: I can filter rows from a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1: **Lab 4 Question 5 - Revised**

```{r}
#| label: wd-3-numeric-ex-1

#Feedback: Amazing column names!!!!
#I would recommend using the %in% operator instead of the or!

median_inc_change <- ca_childcare |> 
  select(county_name, 
         study_year, 
         census_region, 
         mhi_2018) |> 
  filter(study_year %in% c(2008,2018)) |> 
  pivot_wider (names_from = study_year,
               values_from = mhi_2018) |> 
  group_by(census_region) |> 
  summarize(
    median_2018 = median(`2018`),
    median_2008 = median(`2008`),
    .groups = "drop" ) |> 
  arrange(desc(median_2018))

```

-   Numeric Example 2: **Lab 4 Question 6**

```{r}
#| label: wd-3-numeric-ex-2

ca_childcare |> 
  filter(study_year == 2018) |> 
  select (county_name, census_region, mc_infant, study_year) |> 
  group_by(census_region) |> 
  summarize(
    region_median_mc_infant = median(mc_infant),
    .groups = "drop") |> 
  slice_min(region_median_mc_infant) #add this to get the exact answer

```

-   Character Example 1 (any context): **Lab 3 Question 12 - Revised**

```{r}
#| label: wd-3-character

#Feedback: I would recommend using the %in% operator instead of the or!
#Look at your output! You have the same row repeated 6 times! Is there a way to get only one row with this information?

teacher_evals_clean |> 
  filter(academic_degree %in% c("dr","prof"))|>
  group_by(teacher_id, sex, seniority) |>
  summarize(
    avg_percent_resp = mean(resp_share, na.rm = TRUE),
    .groups = "drop")|> 
      filter(avg_percent_resp %in% c(min(avg_percent_resp),max(avg_percent_resp))) |> 
  arrange(desc(avg_percent_resp))

```

-   Character Example 2 (example must use functions from **stringr**): **Lab 5 Find Witnesses - Revised**

```{r}
#| label: wd-3-string

witness2 <- detective |> 
  filter(
    (str_detect(name,
             pattern = "(A|a)nnabel") & address_street_name == "Franklin Ave"))
```

-   Date (example must use functions from **lubridate**): **Modified from Lab 5 Identify Suspects - Revised**

```{r}
#| label: wd-3-date

detective <- detective |> 
mutate(
  check_in_date = ymd(check_in_date)) |> # make check_in_date a date data type so we can use date functions on it!
  filter(membership_status == "gold",
         month(check_in_date) == 1,
         day(check_in_date) == 9,
         str_detect(membership_id,
                    pattern = "^48Z"))
```

**WD-4: I can modify existing variables and create new variables in a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1 **Challenge 7 Question 3**

```{r}
#| label: wd-4-numeric-ex-1
#restrict was a function we previously defined

fishdata <- fishdata |> 
  mutate(
    length = restrict(length, min = 5, max = 80),
    weight = restrict(weight, min = 10, max = 4000)
    )

```

-   Numeric Example 2 **Challenge 3 Question 3**

```{r}
#| label: wd-4-numeric-ex-2


teacher_evals_compare <- teacher_evals |> 
  filter(question_no == 903) |> 
  mutate(
    SET_level = if_else(SET_score_avg >= 4,"excellent", "standard"),
    sen_level = case_when(
                    seniority <= 4 ~ "junior", 
                    seniority <= 8 ~ "senior",
                    seniority > 8 ~ "very senior")) |> 
  select(course_id, SET_level, sen_level)


```

-   Factor Example 1 (renaming levels) **Lab 4 Question 4**

```{r}
#| label: wd-4-factor-ex-1

ca_childcare <- ca_childcare |> 
  mutate(county_name = str_remove(county_name, " County"),
      census_region = fct_collapse(.f = county_name,
               "Superior" = superior_counties,
               "North Coast" = north_coast_counties,
               "San Francisco" = san_fran_counties,
               "North San Joaquin" = n_san_joaquin_counties,
               "Central Coast" = central_coast_counties,
               "South San Joaquin" = s_san_joaquin_counties,
               "Inland" = inland_counties,
               "Los Angeles" = la_county,
               "Orange County" = orange_county,
               "San Diego" = san_diego_imperial_counties ))

```

-   Factor Example 2 (reordering levels) **Lab 4 Question 7 - Revised**

```{r}
#| label: wd-4-factor-ex-2

#Feedback: Nice work pivoting and modifying the age variable! Nice dollar signs!!! Can you reorder the colors in the legend so they appear in the same order as the lines in the plot? I am specifically looking for a tool that does the reordering for you since doing the reordering by hand is not a robust programming practice!

recreate_plot <- ca_childcare |> 
  select(county_name, 
         study_year, 
         mc_infant, 
         mc_toddler, 
         mc_preschool, 
         census_region) |>
  pivot_longer(cols = mc_infant:mc_preschool,
             names_to = "age",
             values_to = "price") |> 
  mutate(age = case_when(age == "mc_infant" ~ "Infant",
                         age == "mc_toddler" ~ "Toddler",
                         age == "mc_preschool" ~ "Preschool",
                         TRUE ~ age),
    census_region = fct_reorder2(.f = census_region, .x = study_year, 
                 .y = price, 
                .desc = TRUE))
```

-   Character (example must use functions from **stringr**) **Lab 5 Identify Suspects - Modified**

```{r}
#| label: wd-4-string

detective |> 
  mutate(
    potential_suspect = if_else(
                    str_detect(membership_id,
                              pattern = "^48Z"),
                        1, 0)
  )

```

-   Date (example must use functions from **lubridate**) **Lab 5 Identify Suspects**

```{r}
#| label: wd-4-date

detective <- detective |> 
mutate(
  check_in_date = ymd(check_in_date)) |> # make check_in_date a date data type
  filter(membership_status == "gold",
         month(check_in_date) == 1,
         day(check_in_date) == 9,
         str_detect(membership_id,
                    pattern = "^48Z"))

```

**WD-5: I can use mutating joins to combine multiple dataframes.**

-   `left_join()` Example 1 **Lab 4 Question 3**

```{r}
#| label: wd-5-left-ex-1

ca_childcare <- left_join(x = ca_childcare,
           y = tax_rev,
          by = join_by(study_year == year, county_name == entity_name))

```

-   `right_join()` Example 1 **Lab 4 Question 3 Revised**

```{r}
#| label: wd-5-right

#modified to be a right join that has the same function as a left join (switched the variables)

ca_childcare <- right_join(x = tax_rev,
           y = ca_childcare,
          by = join_by(study_year == year, county_name == entity_name))

```

-   `left_join()` **or** `right_join()` **Lab 5 Data Join - Revised**

```{r}
#| label: wd-5-left-right-ex-2

detective <- get_fit_now_check_in |> 
    left_join(get_fit_now_member,
        join_by(membership_id == id))

```

-   `inner_join()` Example 1 **Lab 5 Data Join - Revised**

```{r}
#| label: wd-5-inner-ex-1

#this was originally a left join but we want to keep only the values that match to find the suspect, inner join is better

detective <- get_fit_now_check_in |> 
    inner_join(person,
              join_by(person_id == id, name))

```

-   `inner_join()` Example 2 **Lab 4 Question 2**

```{r}
#| label: wd-5-inner-ex-2

ca_childcare <- counties |> 
  filter(state_abbreviation=="CA") |> 
  inner_join(childcare_costs,
            join_by(county_fips_code))

```

**WD-6: I can use filtering joins to filter rows from a dataframe.**

-   `semi_join()` **Lab 5 Witness Interview - Revised**

```{r}
#| label: wd-6-semi

interview |> 
  semi_join(witnesses,
            by = join_by(person_id == id))
```

-   `anti_join()`

```{r}
#| label: wd-6-anti

```

**WD-7: I can pivot dataframes from long to wide and visa versa**

-   `pivot_longer()` **Lab 4 Question 7**

```{r}
#| label: wd-7-long

recreate_plot <- ca_childcare |> 
  select(county_name, 
         study_year, 
         mc_infant, 
         mc_toddler, 
         mc_preschool, 
         census_region) |>
  pivot_longer(cols = mc_infant:mc_preschool,
             names_to = "age",
             values_to = "price") |> 
  mutate(age = case_when(age == "mc_infant" ~ "Infant",
                         age == "mc_toddler" ~ "Toddler",
                         age == "mc_preschool" ~ "Preschool",
                         TRUE ~ age),
    census_region = fct_reorder2(.f = census_region, .x = study_year, 
                 .y = price, 
                .desc = TRUE))

```

-   `pivot_wider()` **Lab 4 Question 5**

```{r}
#| label: wd-7-wide

median_inc_change <- ca_childcare |> 
  select(county_name, 
         study_year, 
         census_region, 
         mhi_2018) |> 
  filter(study_year %in% c(2008,2018)) |> 
  pivot_wider(names_from = study_year,
               values_from = mhi_2018) |> 
  group_by(census_region) |> 
  summarize(
    median_inc_2018 = median(`2018`),
    median_inc_2008 = median(`2008`),
    .groups = "drop" ) |> 
  arrange(desc(median_inc_2018))
```

## Reproducibility - will fill in with more assignments because already submitted revisions

**R-1: I can create professional looking, reproducible analyses using RStudio projects, Quarto documents, and the here package.**

The following assignments satisfy the above criteria:

-   Lab 5: Murder in SQL City
-   Lab 7: Functions + Fish
-   Challenge 7: Incorporating Multiple Inputs
-   Lab 8: Data Frame Functions
-   Lab 9: Searching for Efficiency & Making Great Tables

**R-2: I can write well documented and tidy code.**

-   Example of **ggplot2** plotting **Challenge 3 Question 2**

```{r}
#| label: r-2-1

ggplot(data = teacher_evals_compare, 
      mapping = aes(x = sen_level, 
                    fill = SET_level)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(
    values = c(
       "excellent" = "#B297D0",
       "standard" = "#B49664")) +
  theme_bw() +
  theme(legend.position = "top") +
  labs(
    title= "Evalutation of Teachers' Use of Activities",
      x = "Years of Experience",
      y = NULL,
      fill = "Evaluation Rating")

```

-   Example of **dplyr** pipeline **Lab 4 Question 5**

```{r}
#| label: r-2-2

median_inc_change <- ca_childcare |> 
  select(county_name, 
         study_year, 
         census_region, 
         mhi_2018) |> 
  filter(study_year %in% c(2008,2018)) |> 
  pivot_wider(names_from = study_year,
               values_from = mhi_2018) |> 
  group_by(census_region) |> 
  summarize(
    median_inc_2018 = median(`2018`),
    median_inc_2008 = median(`2008`),
    .groups = "drop" ) |> 
  arrange(desc(median_inc_2018))

```

-   Example of function formatting **Lab 7 Question 4**

```{r}
#| label: r-2-3

rescale_01 <- function(x){
  stopifnot(is.numeric(x))
  if (length(x) < 1) stop("Input vector must have length >= 1!")
  
  rng <- range(x, na.rm = TRUE)
  x = (x - rng[1]) / (rng[2] - rng[1])
}
```

**R-3: I can write robust programs that are resistant to changes in inputs.**

-   Example (any context) **Lab 8 Question 3**

```{r}
#| label: r-3-example

make_title <- function(var){ #helper function!
  str_to_title(
                    str_replace_all(
                            rlang::as_name(enquo(var)),
                            pattern = "_",
                            replacement = " "))
}

plot_color_points <- function(df, x, y, color = NULL) {
   
  x_title <- make_title({{x}})
   y_title <- make_title({{y}})
   
  if(missing(color)){
    label <- str_to_title(str_c("A scatterplot of ", x_title, " and ", y_title))
   
   df |> 
    ggplot(mapping = aes(x = {{x}}, y = {{y}})) +
    geom_point() +
    labs(
      title = label, 
      x = x_title,
      y = y_title)
  }
   
  else{
     color_title <- make_title({{color}})
    
   label <- str_to_title(str_c("A scatterplot of ", x_title, " and ", y_title, ", by ", color_title))
   
   df |> 
    ggplot(mapping = aes(x = {{x}}, y = {{y}}, color = {{color}})) +
    geom_point() +
    labs(
      title = label, 
      x = x_title,
      y = y_title,
      color = color_title)
  }
}
```

-   Example (function stops) **Lab 7 Question 4**

```{r}
#| label: r-3-function-stops

restrict <- function(x, min, max) {
  stopifnot(length(x) >= 1)
  stopifnot("Input 'x' must be a numeric value." = is.numeric(x))

  case_when(x < min ~ NA,
            x > max ~ NA,
            .default = x)
}
```

## Data Visualization & Summarization

**DVS-1: I can create visualizations for a *variety* of variable types (e.g., numeric, character, factor, date)**

-   At least two numeric variables **Lab 10 Question 13**

```{r}
#| label: dvs-1-num

ci_dat |> 
  arrange(estimate) |> 
  mutate(
    cover = as.factor(cover)
  ) |> 
  ggplot(mapping = aes(y = c(1:1000), xmin = conf.low, xmax = conf.high, color = cover)) +
  geom_errorbar() + 
  scale_color_manual(values = RColorBrewer::brewer.pal(9, "Set1")[c(1,3)],
                     labels = c("No",
                                "Yes")) +
  scale_y_continuous(labels = NULL) +
  scale_x_continuous(
             breaks = seq(-2.5, 2.5, by = 0.5)) +
  theme_bw() +
  geom_vline(xintercept = 0.5, linetype = "dashed", alpha = 0.6) +
    labs(
      title = "1000 Confidence Intervals of the mycifun() Function",
      y = NULL,
      color = "Contains True Beta1 = 0.5",
      caption = glue("Proportion Containing True Beta1 = {sum(ci_dat$cover)/length(ci_dat$cover)}")
    )

```

-   At least one numeric variable and one categorical variable **Lab 7 Question 3**

```{r}
#| label: dvs-2-num-cat

mycolors <- RColorBrewer::brewer.pal(12, "Paired")[c(7,12)] # color palette

fishdata |> 
  mutate(
    trip = as.factor(trip),
    year = as.factor(year)) |> 
  group_by(trip, year, section) |> 
    summarize(
      n_NA = sum(is.na(weight)),
      .groups = "drop") |> 
  
ggplot(mapping = aes(x = year, y = n_NA, fill = section)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = n_NA), 
            position = position_dodge(width = 0.9),
            vjust = -0.5, 
            size = 3) +
  facet_wrap(~trip) +
  theme_bw() + 
  theme(
    plot.title = element_text(face = "bold", size = 13)) +
  scale_fill_manual(values = mycolors,
                     labels = c("Jonsrud",
                                "Scotty Brown")) +
  labs(
    title = "Missing Data Between Survey Trips",
    x = "Year",
    y = "Number of Missing Values",
   fill = "River Section")
```

-   At least two categorical variables **Challenge 3 Question 2**

```{r}
#| label: dvs-2-cat

ggplot(data = teacher_evals_compare, 
      mapping = aes(x = sen_level, fill = SET_level)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(
    values = c(
       "excellent" = "#B297D0",
       "standard" = "#B49664")) +
  theme_bw() +
  theme(legend.position = "top") +
  labs(title= "Evalutation of Teachers' Use of Activities",
      x = "Years of Experience",
      y = NULL,
      fill = "Evaluation Rating")
```

-   Dates (time series plot) **Challenge 7 Question 5**

```{r}
#| label: dvs-2-date

mycolors <- RColorBrewer::brewer.pal(12, "Paired")[c(7,12,8,2)] # color palette

fishdata |> 
  mutate(
    condition_index = condition(weight,length),
    species = as.factor(species)) |> 
  group_by(year, species) |> 
  summarize(
    mean_condition = mean(condition_index, na.rm = TRUE),
    .groups = "drop") |>
  mutate(
    species = fct_reorder2(.f = species, .x =year, .y = mean_condition, .desc = TRUE)) |> 
ggplot(mapping = aes(x = year, y = mean_condition, color = species)) +
  geom_rug(sides = "b", color = "#ffdbec", length = unit(100, "npc")) +
  geom_smooth(se = FALSE) +
  geom_point() +
  theme_bw() + 
  scale_color_manual(values = mycolors,
                     labels = c("Rainbow Trout",
                                "Brown Trout",
                                "Westslope Cutthroat Trout",
                                "Bull Trout")) +
  scale_x_continuous(
             breaks = seq(1989, 2006, by = 2)) + # only show every 2 years
  labs(
    title = "Condition Indices of Trout Over Time",
    subtitle = "Mean Condition Index",
    x = "Year",
    y = NULL,
    color = "Trout Species")
```

**DVS-2: I use plot modifications to make my visualization clear to the reader.**

-   I can modify my plot theme to be more readable **Lab 7 Question 3**

```{r}
#| label: dvs-2-ex-1

mycolors <- RColorBrewer::brewer.pal(12, "Paired")[c(7,12)] # color palette

fishdata |> 
  mutate(
    trip = as.factor(trip),
    year = as.factor(year)) |> 
  group_by(trip, year, section) |> 
    summarize(
      n_NA = sum(is.na(weight)),
      .groups = "drop") |> 
  
ggplot(mapping = aes(x = year, y = n_NA, fill = section)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = n_NA), 
            position = position_dodge(width = 0.9),
            vjust = -0.5, 
            size = 3) +
  facet_wrap(~trip) +
  theme_bw() + 
  theme(
    plot.title = element_text(face = "bold", size = 13)) +
  scale_fill_manual(values = mycolors,
                     labels = c("Jonsrud",
                                "Scotty Brown")) +
  labs(
    title = "Missing Data Between Survey Trips",
    x = "Year",
    y = "Number of Missing Values",
   fill = "River Section")
  
```

-   I can modify my colors to be accessible to anyone's eyes **Lab 4 Question 7**

```{r}
#| label: dvs-2-ex-2

mycolors<- colorRampPalette(brewer.pal(7, "Paired"))(10) #The Paired palette is color-deficiency friendly!
  
ggplot(data = recreate_plot, 
        mapping = aes(x = study_year, y = price, color = census_region)) +
        geom_point(size = 0.75) +
        geom_smooth(linewidth = 0.75) +
        facet_wrap(~factor(age, c("Infant", "Toddler", "Preschool"))) +
         scale_y_continuous(labels = label_currency(prefix = "$")) +
         scale_x_continuous(
             breaks = seq(2008, 2018, by = 2),  # only show every 2 years
             limits = c(2008, 2018)) +
        theme_bw(base_size = 10) +
        labs(
          title = "Weekly Median Price for Center-Based Childcare ($)",
           x = "Study Year",
           y = NULL,
           color = "California Region") +
  scale_color_manual(values = mycolors)
```

-   I can modify my plot titles to clearly communicate the data context **Challenge 4 Plot of the Data**

```{r}
#| label: dvs-2-ex-3

ggplot(data = my_research_long, 
        mapping = aes(x = study_year, y = price, color = care_type)) +
        geom_point() +
        geom_smooth(linewidth = 0.75) +
        facet_wrap(~census_region, scales = "free", ncol = 3) +
        scale_y_continuous(labels = label_currency(prefix = "$")) +
        scale_x_continuous(
             breaks = seq(2008, 2018, by = 2)) + # only show every 2 years
        theme_bw(base_size = 12) +
        labs(
          title = "Weekly Median Price for Toddler Childcare for Regions in California ($)",
           x = "Study Year",
           y = NULL,
           color = "Type of Care")
```

-   I can modify the text in my plot to be more readable **Lab 10 Question 3**

```{r}
#| label: dvs-2-ex-4
# change y axis labels to percentages and add the exact percentages on top of the bars

results |> 
enframe() |> 
  count(value) |> 
  mutate(
    n = n/sum(n),
    value = as.factor(value)
  ) |> 
ggplot(mapping = aes(x = value, y = n, fill = value)) +
  geom_col(color = "black",
           linewidth = 0.1 ) +
  geom_text(aes(label = sprintf("%.1f%%", n * 100)), 
            position = position_dodge(width = 0.9),
            vjust = -0.5, 
            size = 3) +
  scale_y_continuous(limits = c(0, 0.40),
                     breaks = seq(0, .40, by = 0.1),
                     labels = label_percent()) +
  theme_bw() + 
  theme(
    plot.title = element_text(face = "bold", size = 13),
    legend.position = "none") +
  labs(
    title = "How Often Babies are Correctly Paired at the Nightmare Hospital",
    subtitle = "Percent Correct",
    x = "# of Correct Pairs",
    y = NULL,
    fill = NULL) +
  scale_fill_manual(
    values = c(
      "0" = "#cfecfc",  
      "1" = "#fccfeb",  
      "2" = "#e6cffc",
      "4" = "#c9f5ce" 
    )
  )
```

-   I can reorder my legend to align with the colors in my plot **Lab 4 Question 7**

```{r}
#| label: dvs-2-ex-5

#reorder legend using fct_reorder and then plotting with ggplot

recreate_plot <- ca_childcare |> 
  select(county_name, 
         study_year, 
         mc_infant, 
         mc_toddler, 
         mc_preschool, 
         census_region) |>
  pivot_longer(cols = mc_infant:mc_preschool,
             names_to = "age",
             values_to = "price") |> 
  mutate(age = case_when(age == "mc_infant" ~ "Infant",
                         age == "mc_toddler" ~ "Toddler",
                         age == "mc_preschool" ~ "Preschool",
                         TRUE ~ age),
    census_region = fct_reorder2(.f = census_region, .x = study_year, #using factor reorder for legend order
                 .y = price, 
                .desc = TRUE))
library(RColorBrewer)

mycolors<- colorRampPalette(brewer.pal(7, "Accent"))(10) #take color palette that has only 7 colors into 10
  
ggplot(data = recreate_plot, 
        mapping = aes(x = study_year, y = price, color = census_region)) + #this will be ordered now
        geom_point(size = 0.75) +
        geom_smooth(linewidth = 0.75) +
        facet_wrap(~factor(age, c("Infant", "Toddler", "Preschool"))) +
         scale_y_continuous(labels = scales::dollar_format(
                                prefix = "$", big.mark = ",")) +
         scale_x_continuous(
             breaks = seq(2008, 2018, by = 2),  # only show every 2 years
             limits = c(2008, 2018)) +
        theme_bw(base_size = 10) +
        theme(aspect.ratio = 1.25, 
              axis.text.x = element_text(angle = 30)) +
        labs(
          title = "Weekly Median Price for Center-Based Childcare ($)",
           x = "Study Year",
           y = NULL,
           color = "California Region") +
  scale_color_manual(values = mycolors)
```

**DVS-3: I show creativity in my visualizations**

-   I can use non-standard colors (Example 1) **Challenge 2 Spicy**

```{r}
#| label: dvs-3-1-ex-1

ggplot(data = surveys, 
        mapping = aes(x = species, y = weight)) +
        geom_jitter(width = 0.2, 
                    height = 0, 
                    alpha = 0.2, 
                    color = "darkseagreen")+
       geom_boxplot(alpha = 0, 
                  color = "darkgreen",
                  outliers = FALSE,
                  median.color= "black",
                  median.linewidth = 0.75, 
                  box.linewidth= 0.25) +
        theme_bw(base_size = 14, base_family = "times new roman") +
   theme(axis.text.x = element_text(angle = 30),
         panel.border = element_rect(colour = "darkgreen", linewidth=2)) +
        labs(
          title = "Comparing Median Weight between Rodent Species",
           x = "Species",
          y = "Weight" 
        )
```

-   I can use non-standard colors (Example 2) - **Challenge 4 Plot of the Data**

```{r}
#| label: dvs-3-1-ex-2

mycoolcolors =colorRampPalette(brewer.pal(7, "Accent"))(10)

ggplot(data = my_research_long, 
        mapping = aes(x = study_year, y = price, color = care_type)) +
        geom_point() +
        geom_smooth(linewidth = 0.75) +
        facet_wrap(~census_region, scales = "free", ncol = 3) +
        scale_y_continuous(labels = scales::dollar_format(prefix = "$", big.mark = ",")) +
        scale_x_continuous(
             breaks = seq(2008, 2018, by = 2)) + # only show every 2 years
        theme_bw(base_size = 12) +
        theme(aspect.ratio = 1.25, axis.text.x = element_text(angle = 30)) +
        labs(
          title = "Weekly Median Price for Toddler Childcare for Regions in California ($)",
           x = "Study Year",
           y = NULL,
           color = "Type of Care") +
      scale_color_manual(values = mycoolcolors)
        
```

-   I can use annotations (e.g., `geom_text()`)

```{r}
#| label: dvs-3-2

results |> 
enframe() |> 
  count(value) |> 
  mutate(
    n = n/sum(n),
    value = as.factor(value)
  ) |> 
ggplot(mapping = aes(x = value, y = n, fill = value)) +
  geom_col(color = "black",
           linewidth = 0.1 ) +
  geom_text(aes(label = sprintf("%.1f%%", n * 100)), 
            position = position_dodge(width = 0.9),
            vjust = -0.5, 
            size = 3) +
  scale_y_continuous(limits = c(0, 0.40),
                     breaks = seq(0, .40, by = 0.1),
                     labels = label_percent()) +
  theme_bw() + 
  theme(
    plot.title = element_text(face = "bold", size = 13),
    legend.position = "none") +
  labs(
    title = "How Often Babies are Correctly Paired at the Nightmare Hospital",
    subtitle = "Percent Correct",
    x = "# of Correct Pairs",
    y = NULL,
    fill = NULL) +
  scale_fill_manual(
    values = c(
      "0" = "#cfecfc",  
      "1" = "#fccfeb",  
      "2" = "#e6cffc",
      "4" = "#c9f5ce" 
    )
  )
```

-   I can choose creative geometries (e.g., `geom_segment()`, `geom_ribbon)()`)

```{r}
#| label: dvs-3-3

ci_dat |> 
  arrange(estimate) |> 
  mutate(
    cover = as.factor(cover)
  ) |> 
  ggplot(mapping = aes(y = c(1:1000), xmin = conf.low, xmax = conf.high, color = cover)) +
  geom_errorbar() + 
  scale_color_manual(values = RColorBrewer::brewer.pal(9, "Set1")[c(1,3)],
                     labels = c("No",
                                "Yes")) +
  scale_y_continuous(labels = NULL) +
  scale_x_continuous(
             breaks = seq(-2.5, 2.5, by = 0.5)) +
  theme_bw() +
  geom_vline(xintercept = 0.5, linetype = "dashed", alpha = 0.6) +
    labs(
      title = "1000 Confidence Intervals of the mycifun() Function",
      y = NULL,
      color = "Contains True Beta1 = 0.5",
      caption = glue("Proportion Containing True Beta1 = {sum(ci_dat$cover)/length(ci_dat$cover)}")
    )
```

**DVS-4: I can calculate numerical summaries of variables.**

-   Example using `summarize()` **Lab 3 Question 6**

```{r}
#| label: dvs-4-summarize

teacher_evals_clean |>
  summarize(
    courses = n_distinct(course_id),
    teachers = n_distinct(teacher_id)
  )
```

-   Example using `across()` - **Lab 7 Question 1**

```{r}
#| label: dvs-4-across

fishdata |> 
  summarize(
    across(
      .cols = everything(),
      .fns = ~ sum(is.na(.x))
  ))
```

**DVS-5: I can find summaries of variables across multiple groups.**

-   Example 1 **Lab 3 Question 12**

```{r}
#| label: dvs-5-1

#Feedback: I would recommend using the %in% operator instead of the or! Look at your output! You have the same row repeated 6 times! Is there a way to get only one row with this information?

teacher_evals_clean |> 
  filter(academic_degree %in% c("dr","prof"))|>
  group_by(teacher_id, sex, seniority) |>
  summarize(
    avg_percent_resp = mean(resp_share, na.rm = TRUE),
    .groups = "drop")|> 
      filter(avg_percent_resp %in% c(min(avg_percent_resp),max(avg_percent_resp))) |> 
  arrange(desc(avg_percent_resp))
```

-   Example 2 **Lab 4 Question 5**

```{r}
#| label: dvs-5-2

median_inc_change <- ca_childcare |> 
  select(county_name, 
         study_year, 
         census_region, 
         mhi_2018) |> 
  filter(study_year %in% c(2008,2018)) |> 
  pivot_wider (names_from = study_year,
               values_from = mhi_2018) |> 
  group_by(census_region) |> 
  summarize(
    median_inc_2018 = median(`2018`),
    median_inc_2008 = median(`2008`),
    .groups = "drop" ) |> 
  arrange(desc(median_inc_2018))
```

**DVS-6: I can create tables which make my summaries clear to the reader.**

-   I can modify my column names to clearly communicate the data context **Lab 9 Question 2**

```{r}
#| label: dvs-6-ex-1
#| 
surveys |> 
  map_chr(.f = ~ class(.x)) |> 
  enframe() |> 
  mutate(
    name = str_to_title(str_replace_all(name, 
                pattern = "_", 
                replacement = " ")),
    value = str_to_title(value)) |> 
  kable(
  col.names = c("Variable", "Data Type"),
  align = 'c',
  caption = "Data Types in the Surveys Dataset") |> 
  kable_classic(full_width = F, html_font = "Cambria")
```

-   I can modify the text in my table to be more readable (e.g., bold face for column headers) **Lab 9 Question 3**

```{r}
#| label: dvs-6-ex-2

surveys |> 
  map_chr(.f = ~ class(.x)) |> 
  enframe() |> 
  arrange(value) |> 
  mutate(
    name = str_to_title(str_replace_all(name,  
                pattern = "_", 
                replacement = " ")),
    value = str_to_title(value)) |> 
  kable(
  col.names = c("Variable", "Data Type"),
  align = 'c',
  caption = "Data Types in the Surveys Dataset") |> 
  kable_styling(full_width = FALSE,
                bootstrap_options = "striped")
```

-   I can arrange my table to have an intuitive ordering **Lab 9 Question 6**

```{r}
#| label: dvs-6-ex-3
#table is ordered by groups

evals_table |>
  gt(groupname_col = "variable") |> 
  tab_header(
    title = "Instructor Demographics",
    subtitle = "From Student Evaluations at the University of Poland, Warsaw in 2020"
  ) |>
  fmt_percent(
    columns = prop,
    decimals = 2
  ) |> 
    cols_label(
    level = md("**Demographic**"),
    n = md("**Count**"),
    prop = md("**%**")) |> 
  tab_spanner(
    label = "Professors",
    columns = c(n, prop))|> 
  tab_style(
    style = cell_fill(color = "#cce3af"),
    locations = list(cells_row_groups(everything()), cells_title(groups = "title"))) |> 
   tab_style(
    style = cell_borders(
      sides = c("t", "b", "l", "r"),
      color = "black",
      weight = px(2)),
    locations = list(cells_column_labels(), cells_stubhead(), cells_title(), cells_body(), cells_row_groups(), cells_column_spanners())
  ) |> 
  tab_style(
    style = cell_text(font = system_fonts(name = "classical-humanist")),
    locations = list(cells_body(), cells_column_labels(), cells_title(), cells_row_groups())
  )
```

**DVS-7: I show creativity in my tables.**

-   I can use non-default colors **Lab 9 Question 8**

```{r}
#| label: dvs-7-ex-1

fish |> 
  map_int(.f = ~ sum(is.na(.x))) |> 
  enframe() |> 
  mutate(
    name = str_to_title(name)
  ) |> 
  arrange(value, name) |> 
  gt() |> 
  data_color(
    method = "numeric",
    palette = RColorBrewer::brewer.pal(3, "Set1")[c(3,1)]) |> 
  tab_header(
    title = md("**Missing Values for Fish Measurements**"),
    subtitle = "1989-2006 - Blackfoot Fish River in Montana"
  ) |> 
  cols_label(
    name = md("**Variable**"),
    value = md("**Number Missing**")
  ) |> 
  tab_style(
    style = cell_borders(
      sides = c("t", "b", "l", "r"),
      color = "black",
      weight = px(2)),
    locations = list(cells_column_labels(), cells_stubhead(), cells_title(), cells_body())
  ) |> 
  tab_style(
    style = cell_text(font = system_fonts(name = "classical-humanist")),
    locations = list(cells_body(), cells_column_labels(), cells_title())
  )
```

-   I can modify the layout of my table to be more readable (e.g., `pivot_longer()` or `pivot_wider()`) **Lab 9 Question 5**

```{r}
#| label: dvs-7-ex-2

evals_table <- evals |> 
  distinct(teacher_id, academic_degree, seniority, sex) |> 
  mutate(
   seniority = case_when(seniority <= 4 ~ "junior", 
                    .default = "senior")) |> 
  pivot_longer(
    c(academic_degree, seniority, sex),
    names_to  = "variable",
    values_to = "level"
  ) |> 
  mutate(
    variable = str_to_title(str_replace(variable,
                                        pattern = "_",
                                        replacement = " ")),
    level = case_when(level == "no_dgr" ~ "No Degree",
                      level == "ma" ~ "Masters",
                      level == "dr" ~ "Doctorate",
                      level == "prof" ~ "Tenured Professor",
                      .default = level),
    level = str_to_title(level)) |> 
  count(variable, level, name = "n") |> 
  group_by(variable) |> 
  mutate(
    prop = n/sum(n)) |> 
  ungroup()
  
```

## Program Efficiency

**PE-1: I can write concise code which does not repeat itself.**

-   using a single function call with multiple inputs (rather than multiple function calls) **Lab 5 Identify Murderer**

```{r}
#| label: pe-1-one-call

detective |> 
  filter(hair_color == "red", 
         gender == "female", 
         car_make == "Tesla", 
         car_model == "Model S", 
         between(height, 65, 67), 
         event_name == "SQL Symphony Concert") |> 
  summarize(name)

```

-   using `across()` - **Lab 3 Question 8**

```{r}
#| label: pe-1-across

teacher_evals_clean |>
  filter(if_any(
    .cols = everything(), 
    .fns = ~ is.na(.x)))
```

-   using functions from the `map()` family **Lab 9 Question 4**

```{r}
#| label: pe-1-map-1

evals <- evals |> 
  map_if(.x = evals,
         .p = is.character,
         .f = ~ as.factor(.x)) |> 
  bind_cols()
```

**PE-2: I can write functions to reduce repetition in my code.**

-   Example 1: Function that operates on vectors - **Challenge 7 Question 2**

```{r}
#| label: pe-2-1

restrict <- function(x, min, max) {
  stopifnot("Input 'x' must be a numeric value." = is.numeric(x))
  if (length(x) < 1) stop("Input vector must have length >= 1!")
  
  case_when(x < min ~ NA,
            x > max ~ NA,
            .default = x)
}
```

-   Example 2: Function that operates on data frames **Lab 8 Question 1**

```{r}
#| label: pe-2-2

rescale_column <- function(df, cols){
  df |> 
   mutate(
       across(.cols = {{cols}},
              .fns = ~ rescale_01(.x)
              )
       )
}
```

-   Example 3: Function that operates on vectors *or* data frames **Lab 7 Question 4**

```{r}
#| label: pe-2-3

rescale_01 <- function(x){
  stopifnot(is.numeric(x))
  if (length(x) < 1) stop("Input vector must have length >= 1!")
  rng <- range(x, na.rm = TRUE)
  x = (x - rng[1]) / (rng[2] - rng[1])
}
```

**PE-3: I can use iteration to reduce repetition in my code.**

-   using `across()` **Lab 7 Question 1**

```{r}
#| label: pe-3-across


```

-   using a `map()` function with **one** input (e.g., `map()`, `map_chr()`, `map_dbl()`, etc.) **Lab 9 Question 2**

```{r}
#| label: pe-3-map-1

surveys |> 
  map_chr(.f = ~ class(.x)) |> 
  enframe() |> 
  mutate(
    name = str_to_title(str_replace_all(name, 
                pattern = "_", 
                replacement = " ")),
    value = str_to_title(value)) |> 

  kable(
  col.names = c("Variable", "Data Type"),
  align = 'c',
  caption = "Data Types in the Surveys Dataset") |> 
  kable_classic(full_width = F, html_font = "Cambria")
```

-   using a `map()` function with one input

```{r}
#| label: pe-3-map-2


```

**PE-4: I can use modern tools when carrying out my analysis.**

-   I can use functions which are not superseded or deprecated **Lab 4 Question 7**

```{r}
#| label: pe-4-1

ggplot(data = recreate_plot, 
        mapping = aes(x = study_year, y = price, color = census_region)) +
        geom_point(size = 0.75) +
        geom_smooth(linewidth = 0.75) +
        facet_wrap(~factor(age, c("Infant", "Toddler", "Preschool"))) +
         scale_y_continuous(labels = label_currency(prefix = "$")) + #modern label function
         scale_x_continuous(
             breaks = seq(2008, 2018, by = 2),  # only show every 2 years
             limits = c(2008, 2018)) +
        theme_bw(base_size = 10) +
        labs(
          title = "Weekly Median Price for Center-Based Childcare ($)",
           x = "Study Year",
           y = NULL,
           color = "California Region") +
  scale_color_manual(values = mycolors)
```

-   I can connect a data wrangling pipeline into a `ggplot()` **Lab 7 Question 3**

```{r}
#| label: pe-4-2

fishdata |> 
  mutate(
    trip = as.factor(trip),
    year = as.factor(year)) |> 
  group_by(trip, year, section) |> 
    summarize(
      n_NA = sum(is.na(weight)),
      .groups = "drop") |> 
ggplot(mapping = aes(x = year, y = n_NA, fill = section)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = n_NA), 
            position = position_dodge(width = 0.9),
            vjust = -0.5, 
            size = 3) +
  facet_wrap(~trip) +
  theme_bw() + 
  theme(
    plot.title = element_text(face = "bold", size = 13)) +
  scale_fill_manual(values = mycolors,
                     labels = c("Jonsrud",
                                "Scotty Brown")) +
  labs(
    title = "Missing Data Between Survey Trips",
    x = "Year",
    y = "Number of Missing Values",
   fill = "River Section")
```

## Data Simulation & Statisticalac Models

**DSSM-1: I can simulate data from a *variety* of probability models.**

-   Example 1 **Lab 10 Question 4**

```{r}
#| label: dsm-1-1

randomBabies <- function(n_babies){
  
  baby <- tibble(correct_parent = 1:n_babies,
                 new_parent = sample(1:n_babies,
                                     size = n_babies,
                                     replace = FALSE))
  correct_pairs <- baby |>
    filter(correct_parent == new_parent) |> 
    nrow()
  
  correct_pairs
  
}
```

-   Example 2 **Lab 10 Question 4**

```{r}
#| label: dsm-1-2

set.seed(525600)

# define slope and intercept parameters
intercept = 2
slope = 1

# generate x vector
x = runif(n = 100,
      min= 0,
      max = 1)

# generate noise `ep` vector
ep = rnorm(n = 100,
      mean = 0,
      sd = 1)

# generate outcome from population model
y = intercept + x*slope + ep


# create an "observed data" dataframe with only the x and y vectors
obs_data <- tibble(y,
                   x)
```

**DSSM-2: I can conduct common statistical analyses in R.**

-   Example 1 **Lab 10 Question 7**

```{r}
#| label: dsm-2-1

mod <- lm(y ~ x, data = obs_data)
```

-   Example 2 **Lab 3 Question 3**

```{r}
#| label: dsm-2-2

chisq.test(teacher_evals_compare$SET_level, teacher_evals_compare$sen_level)
```

-   Example 3 **Lab 2 Question 17**

```{r}
#| label: dsm-2-3

aov(weight ~ species, data = surveys)
```

## Revising My Thinking

<!-- How did you revise your thinking throughout the course? How did you revise your thinking on the code examples you have provided in your portfolio? -->

I've definitely learned that there is often an easier way to certain perform tasks when I am aware of the correct functions. This takes practice, but I think I am growing in recognizing shortcuts better to have more efficient code. I revised my thinking my starting from square 1 on many problems, and envisioning the different ways to attack a problem. I use feedback from every assignment to submit thoughtful revisions for every single assignment when available. I do my best to implement what I have learned from revisions into my future work.

<!-- For the revisions included in your Portfolio, to help me understand the nature of your revisions, please denote somehow the feedback I provided you (e.g., boldface, italics, colored text) before your revisions. -->

## Extending My Thinking

<!-- How did you extended your thinking throughout the course? How did you extend your thinking on the code examples you have provided in your portfolio? -->

I have extended my thinking by constantly searching through resources and Stack Overflow for more efficient solutions to problems. I like to be creative with my plots, so I tried my best to customize as much as possible using outside research and the tools at my disposal. I think I went above and beyond when it came to open-ended analysis because this is the kind of work that I want to be doing in the future. I am really trying to hone these skills so I can be prepared and make clear visualizations and reports.

## Peer Support & Collaboration

<!-- Include an image or a description of feedback you gave that you are proud of (either in a peer review or in Discord). -->

My feedback:

"First of all, I love the theme of your output! The white font is a little small and hard to read on the background but still super cute!"

"Make sure when you load in your data and libraries that you put {r, message=FALSE} in each code chunk to silence the messages. It took me forever to figure out where to put it, but it helps readability!"

I think it is really important to lift people up for going the extra mile for creativity. I also makes me feel really good in a peer review when I know that I am struggling through concepts alongside my fellow students. That makes the advice even more valuable. It took me a long time to consistently have professional report skills, so I wanted to share that knowledge.

<!-- Include a description of how you grew as a collaborator through the weekly pair programming activities.   -->

It was difficult to be the "computer" role during collaboration because I wanted to give the answer to the problem immediately when I identify it. However, I think that I learn best when challenged in the role of the coder, so I do my best to honor that experience for others. Having mutual respect for the process of trial and error with another partner has really garnered a positive space to grow. I think I am doing a good job at asking questions and helping others to find solutions on their own!

## Grade Reasoning

I believe that I deserve an A- on this midterm portfolio because I have fine-tuned each code chunk to achieve the goal of the learning target. I have also updates code chunks from past assignments to include shortcuts and modern tools that I would not have known at the time such as the %in% operator. I take extra time to show my creativity, ask questions to better my understanding, and effectively implement new skills as a I learn them. For these reasons, I believe that an A- is the proper grade for this midterm portfolio, as I am not perfect, but getting very close to consistently efficient and tidy code!
