---
title: "STAT 331 Portfolio"
author: "Elise Donaho"
theme: minty
format:
  html:
    toc: true
embed-resources: true
layout: margin-left
editor: visual
execute: 
  eval: false
  error: true
  echo: true
  warnings: false
---

[**My Grade:**]{.underline} I believe my grade equivalent to course work evidenced below to be an A.

## Working with Data

**WD-1: I can import data from a *variety* of formats (e.g., csv, xlsx, txt, etc.).**

-   `csv` Example 1: **Lab 3 Question 2**

```{r}
#| label: wd-1-csv-1

#using the here::here function to easily look for files already put into the working directory

teacher_evals <- read_csv(here::here("Week 3", "teacher_evals.csv"))

```

-   `csv` Example 2: **Lab 2 Question 1**

```{r}
#| label: wd-1-csv-2

surveys <- read_csv(here::here("Week 2", "surveys.csv"))

```

-   `xlsx:`**Check-In 2.3: Loading Data**

```{r}
#| label: wd-1-xlsx

ages <- read_excel(here::here("ages.xlsx"))
```

**WD-2: I can select necessary columns from a dataset.**

-   Example selecting specified columns: **Lab 3 Question 5**

```{r}
#| label: wd-2-ex-1

teacher_evals_clean <- teacher_evals |> 
  rename(sex = gender) |>
  filter(no_participants >= 10) |>
  mutate(
    teacher_id = as.character(teacher_id),
    course_id = as.character(course_id)
    ) |> 
  select(course_id, 
         teacher_id, 
         question_no, 
         no_participants, 
         resp_share, #<- selecting solely these columns
         SET_score_avg, 
         percent_failed_cur, 
         academic_degree, 
         seniority, sex)

```

-   Example removing specified columns: **Lab 3 Question 5 - Modified**

```{r}
#| label: wd-2-ex-2

teacher_evals_clean <- teacher_evals |> 
  rename(sex=gender) |>
  filter(no_participants >= 10) |>
  mutate(
    teacher_id = as.character(teacher_id),
    course_id = as.character(course_id)
    ) |> 
  select(-course_id,
         -teacher_id, #selecting all columns BUT these 3 (removing the 3)
         -question_no)
```

-   Example selecting columns based on logical values (e.g., `starts_with()`, `ends_with()`, `contains()`, `where()`) **Lab 4 Question 7**

```{r}
#| label: wd-2-ex-3

recreate_plot <- ca_childcare |> 
  select(county_name, 
         study_year, 
         starts_with("mc_"), # find columns that have names that start with mc_
         census_region) |>
  pivot_longer(cols = mc_infant:mc_preschool,
             names_to = "age",
             values_to = "price") |> 
  mutate(age = case_when(age == "mc_infant" ~ "Infant",
                         age == "mc_toddler" ~ "Toddler",
                         age == "mc_preschool" ~ "Preschool",
                         TRUE ~ age),
    census_region = fct_reorder2(.f = census_region, .x = study_year, 
                 .y = price, 
                .desc = TRUE))
```

**WD-3: I can filter rows from a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1: **Lab 4 Question 5 - Revised**

```{r}
#| label: wd-3-numeric-ex-1

#Feedback: Amazing column names!!!!
#I would recommend using the %in% operator instead of the or!

median_inc_change <- ca_childcare |> 
  select(county_name, 
         study_year, 
         census_region, 
         mhi_2018) |> 
  filter(study_year %in% c(2008,2018)) |> 
  pivot_wider (names_from = study_year,
               values_from = mhi_2018) |> 
  group_by(census_region) |> 
  summarize(
    median_inc_2018 = median(`2018`),
    median_inc_2008 = median(`2008`),
    .groups = "drop" ) |> 
  arrange(desc(median_inc_2018))

```

-   Numeric Example 2: **Lab 4 Question 6**

```{r}
#| label: wd-3-numeric-ex-2

ca_childcare |> 
  filter(study_year == 2018) |> 
  select (county_name, census_region, mc_infant, study_year) |> 
  group_by(census_region) |> 
  summarize(
    region_median_mc_infant = median(mc_infant),
    .groups = "drop") |> 
  slice_min(region_median_mc_infant) #add this to get the exact answer

```

-   Character Example 1 (any context): **Lab 3 Question 12 - Revised**

```{r}
#| label: wd-3-character

#Feedback: I would recommend using the %in% operator instead of the or!
#Look at your output! You have the same row repeated 6 times! Is there a way to get only one row with this information?

teacher_evals_clean |> 
  filter(academic_degree %in% c("dr","prof"))|>
  group_by(teacher_id, sex, seniority) |>
  summarize(
    avg_percent_resp = mean(resp_share, na.rm = TRUE),
    .groups = "drop")|> 
      filter(avg_percent_resp %in% c(min(avg_percent_resp),max(avg_percent_resp))) |> 
  arrange(desc(avg_percent_resp))

```

-   Character Example 2 (example must use functions from **stringr**): **Lab 5 Find Witnesses - Revised**

```{r}
#| label: wd-3-string

witness2 <- detective |> 
  filter(
    (str_detect(name,
             pattern = "(A|a)nnabel") & address_street_name == "Franklin Ave"))
```

-   Date (example must use functions from **lubridate**): **Lab 5 Identify Suspects - Revised**

```{r}
#| label: wd-3-date

detective <- detective |> 
mutate(
  check_in_date = ymd(check_in_date)) |> # make check_in_date a date data type so we can use date functions on it!
  filter(membership_status == "gold",
         month(check_in_date) == 1,
         day(check_in_date) == 9,
         str_detect(membership_id,
                    pattern = "^48Z"))
```

**WD-4: I can modify existing variables and create new variables in a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1 **Challenge 7 Question 3**

```{r}
#| label: wd-4-numeric-ex-1
#restrict was a function we previously defined

fishdata <- fishdata |> 
  mutate(
    length = restrict(length, min = 5, max = 80),
    weight = restrict(weight, min = 10, max = 4000)
    )

```

-   Numeric Example 2 **Challenge 3 Question 3**

```{r}
#| label: wd-4-numeric-ex-2


teacher_evals_compare <- teacher_evals |> 
  filter(question_no == 903) |> 
  mutate(
    SET_level = if_else(SET_score_avg >= 4,"excellent", "standard"),
    sen_level = case_when(
                    seniority <= 4 ~ "junior", 
                    seniority <= 8 ~ "senior",
                    seniority > 8 ~ "very senior")) |> 
  select(course_id, SET_level, sen_level)


```

-   Factor Example 1 (renaming levels) **Lab 4 Question 4**

```{r}
#| label: wd-4-factor-ex-1

ca_childcare <- ca_childcare |> 
  mutate(county_name = str_remove(county_name, " County"),
      census_region = fct_collapse(.f = county_name,
               "Superior" = superior_counties,
               "North Coast" = north_coast_counties,
               "San Francisco" = san_fran_counties,
               "North San Joaquin" = n_san_joaquin_counties,
               "Central Coast" = central_coast_counties,
               "South San Joaquin" = s_san_joaquin_counties,
               "Inland" = inland_counties,
               "Los Angeles" = la_county,
               "Orange County" = orange_county,
               "San Diego" = san_diego_imperial_counties ))

```

-   Factor Example 2 (reordering levels) **Lab 4 Question 7 - Revised**

```{r}
#| label: wd-4-factor-ex-2

#Feedback: Nice work pivoting and modifying the age variable! Nice dollar signs!!! Can you reorder the colors in the legend so they appear in the same order as the lines in the plot? I am specifically looking for a tool that does the reordering for you since doing the reordering by hand is not a robust programming practice!

recreate_plot <- ca_childcare |> 
  select(county_name, 
         study_year, 
         mc_infant, 
         mc_toddler, 
         mc_preschool, 
         census_region) |>
  pivot_longer(cols = mc_infant:mc_preschool,
             names_to = "age",
             values_to = "price") |> 
  mutate(age = case_when(age == "mc_infant" ~ "Infant",
                         age == "mc_toddler" ~ "Toddler",
                         age == "mc_preschool" ~ "Preschool",
                         TRUE ~ age),
    census_region = fct_reorder2(.f = census_region, .x = study_year, 
                 .y = price, 
                .desc = TRUE))
```

-   Character (example must use functions from **stringr**) **Lab 5 Identify Suspects - Modified**

```{r}
#| label: wd-4-string

detective |> 
  mutate(
    potential_suspect = if_else(
                    str_detect(membership_id,
                              pattern = "^48Z"),
                        1, 0)
  )

```

-   Date (example must use functions from **lubridate**) **Lab 5 Identify Suspects**

```{r}
#| label: wd-4-date

detective <- detective |> 
mutate(
  check_in_date = ymd(check_in_date)) |> # make check_in_date a date data type
  filter(membership_status == "gold",
         month(check_in_date) == 1,
         day(check_in_date) == 9,
         str_detect(membership_id,
                    pattern = "^48Z"))

```

**WD-5: I can use mutating joins to combine multiple dataframes.**

-   `left_join()` Example 1 **Lab 4 Question 3**

```{r}
#| label: wd-5-left-ex-1

ca_childcare <- left_join(x = ca_childcare,
           y = tax_rev,
          by = join_by(study_year == year, county_name == entity_name))

```

-   `right_join()` Example 1 **Lab 4 Question 3 Revised**

```{r}
#| label: wd-5-right

#modified to be a right join that has the same function as a left join (switched the variables)

ca_childcare <- right_join(x = tax_rev,
           y = ca_childcare,
          by = join_by(study_year == year, county_name == entity_name))

```

-   `left_join()` **or** `right_join()` **Lab 5 Data Join - Revised**

```{r}
#| label: wd-5-left-right-ex-2

detective <- get_fit_now_check_in |> 
    left_join(get_fit_now_member,
        join_by(membership_id == id))

```

-   `inner_join()` Example 1 **Lab 5 Data Join - Revised**

```{r}
#| label: wd-5-inner-ex-1

#this was originally a left join but we want to keep only the values that match to find the suspect, inner join is better

detective <- get_fit_now_check_in |> 
    inner_join(person,
              join_by(person_id == id, name))

```

-   `inner_join()` Example 2 **Lab 4 Question 2 - Modified**

```{r}
#| label: wd-5-inner-ex-2

ca_childcare <- counties |> 
  filter(state_abbreviation=="CA") |> 
  inner_join(childcare_costs,
            join_by(county_fips_code))

```

**WD-6: I can use filtering joins to filter rows from a dataframe.**

-   `semi_join()` **Lab 5 Witness Interview - Revised**

```{r}
#| label: wd-6-semi
#Revision: create a data frame containing the witnesses and filter the interview set by that dataframe to find their interviews

witnesses <- person |> 
  filter(address_street_name == "Northwestern Dr" & 
          address_number == max(address_number[address_street_name == "Northwestern Dr"]) | 
           str_detect(name,
                      pattern = "(A|a)nnabel") & address_street_name == "Franklin Ave")

interview |> 
  semi_join(witnesses,
            by = join_by(person_id == id))
```

-   `anti_join()` **Lab 5 Witness Interview - Modified**

```{r}
#| label: wd-6-anti
#create a dataframe with all the people who are NOT witnesses and then filter anti join to leave only the rows that don't match (the witnesses)

notwitnesses <- person |> 
  filter(!(address_street_name == "Northwestern Dr" & 
          address_number == max(address_number[address_street_name == "Northwestern Dr"]) | 
           str_detect(name,
                      pattern = "(A|a)nnabel") & address_street_name == "Franklin Ave"))

interview |> 
  anti_join(notwitnesses,
            by = join_by(person_id == id))

```

**WD-7: I can pivot dataframes from long to wide and visa versa**

-   `pivot_longer()` **Lab 4 Question 7 - Revised**

```{r}
#| label: wd-7-long

#Feedback: Can you reorder the colors in the legend so they appear in the same order as the lines in the plot? I am specifically looking for a tool that does the reordering for you since doing the reordering by hand is not a robust programming practice!

#this is the data preparation for a plot recreation

recreate_plot <- ca_childcare |> 
  select(county_name, 
         study_year, 
         mc_infant, 
         mc_toddler, 
         mc_preschool, 
         census_region) |>
  pivot_longer(cols = mc_infant:mc_preschool,
             names_to = "age",
             values_to = "price") |> 
  mutate(age = case_when(age == "mc_infant" ~ "Infant",
                         age == "mc_toddler" ~ "Toddler",
                         age == "mc_preschool" ~ "Preschool",
                         TRUE ~ age),
    census_region = fct_reorder2(.f = census_region, .x = study_year, 
                 .y = price, 
                .desc = TRUE))

```

-   `pivot_wider()` **Lab 4 Question 5**

```{r}
#| label: wd-7-wide

#Feedback: Amazing column names!!!!
#I would recommend using the %in% operator instead of the or!

median_inc_change <- ca_childcare |> 
  select(county_name, 
         study_year, 
         census_region, 
         mhi_2018) |> 
  filter(study_year %in% c(2008,2018)) |> 
  pivot_wider(names_from = study_year,
               values_from = mhi_2018) |> 
  group_by(census_region) |> 
  summarize(
    median_inc_2018 = median(`2018`),
    median_inc_2008 = median(`2008`),
    .groups = "drop" ) |> 
  arrange(desc(median_inc_2018))
```

## Reproducibility

**R-1: I can create professional looking, reproducible analyses using RStudio projects, Quarto documents, and the here package.**

The following assignments satisfy the above criteria:

-   Lab 7: Functions + Fish
-   Challenge 7: Incorporating Multiple Inputs
-   Lab 8: Data Frame Functions
-   Lab 9: Searching for Efficiency & Making Great Tables
-   Lab 10: Simulation Exploration

**R-2: I can write well documented and tidy code.**

-   Example of **ggplot2** plotting **Challenge 3 Question 2**

```{r}
#| label: r-2-1
#Success Feedback: Incredible work! Nice job matching the colors, the percentage labels, and the legend position!

ggplot(data = teacher_evals_compare, 
      mapping = aes(x = sen_level, 
                    fill = SET_level)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(
    values = c(
       "excellent" = "#B297D0",
       "standard" = "#B49664")) +
  theme_bw() +
  theme(legend.position = "top") +
  labs(
    title= "Evalutation of Teachers' Use of Activities",
      x = "Years of Experience",
      y = NULL,
      fill = "Evaluation Rating")

```

-   Example of **dplyr** pipeline **Lab 4 Question 5**

```{r}
#| label: r-2-2
#Feedback:Amazing column names!!!!
#I would recommend using the %in% operator instead of the or!

median_inc_change <- ca_childcare |> 
  select(county_name, 
         study_year, 
         census_region, 
         mhi_2018) |> 
  filter(study_year %in% c(2008,2018)) |> 
  pivot_wider(names_from = study_year,
               values_from = mhi_2018) |> 
  group_by(census_region) |> 
  summarize(
    median_inc_2018 = median(`2018`),
    median_inc_2008 = median(`2008`),
    .groups = "drop" ) |> 
  arrange(desc(median_inc_2018))

```

-   Example of function formatting **Lab 7 Question 4**

```{r}
#| label: r-2-3

rescale_01 <- function(x){
  stopifnot(is.numeric(x))
  if (length(x) < 1) stop("Input vector must have length >= 1!")
  
  rng <- range(x, na.rm = TRUE)
  x = (x - rng[1]) / (rng[2] - rng[1])
}
```

**R-3: I can write robust programs that are resistant to changes in inputs.**

-   Example (any context) **Lab 8 Question 3**

```{r}
#| label: r-3-example

#Feedback: It looks like you are doing the same process for all your labels! Maybe you could write a helper function?!

#Nice work incorporating function checks for what inputs your function expects!

make_title <- function(var){ #helper function!
  str_to_title(
                    str_replace_all(
                            rlang::as_name(enquo(var)),
                            pattern = "_",
                            replacement = " "))
}

plot_color_points <- function(df, x, y, color = NULL) {
   
  x_title <- make_title({{x}})
   y_title <- make_title({{y}})
   
  if(missing(color)){
    label <- str_to_title(str_c("A scatterplot of ", x_title, " and ", y_title))
   
   df |> 
    ggplot(mapping = aes(x = {{x}}, y = {{y}})) +
    geom_point() +
    labs(
      title = label, 
      x = x_title,
      y = y_title)
  }
   
  else{
     color_title <- make_title({{color}})
    
   label <- str_to_title(str_c("A scatterplot of ", x_title, " and ", y_title, ", by ", color_title))
   
   df |> 
    ggplot(mapping = aes(x = {{x}}, y = {{y}}, color = {{color}})) +
    geom_point() +
    labs(
      title = label, 
      x = x_title,
      y = y_title,
      color = color_title)
  }
}
```

-   Example (function stops) **Lab 7 Question 4**

```{r}
#| label: r-3-function-stops

restrict <- function(x, min, max) {
  stopifnot(length(x) >= 1)
  stopifnot("Input 'x' must be a numeric value." = is.numeric(x))

  case_when(x < min ~ NA,
            x > max ~ NA,
            .default = x)
}
```

## Data Visualization & Summarization

**DVS-1: I can create visualizations for a *variety* of variable types (e.g., numeric, character, factor, date)**

-   At least two numeric variables **Lab 10 Question 13**

```{r}
#| label: dvs-1-num
#Feedback: Arranged confidence intervals! Nice work!

#Red and green are hard for some people’s eyes to differentiate! Can you modify your colors to be more acccesible for everyone’s eyes?

#revised: changed to red and blue
ci_dat |> 
  arrange(estimate) |> 
  mutate(
    cover = as.factor(cover)
  ) |> 
  ggplot(mapping = aes(y = c(1:1000), xmin = conf.low, xmax = conf.high, color = cover)) +
  geom_errorbar() + 
  scale_color_manual(values = RColorBrewer::brewer.pal(9, "Set1")[c(1,2)],
                     labels = c("No",
                                "Yes")) +
  scale_y_continuous(labels = NULL) +
  scale_x_continuous(
             breaks = seq(-2.5, 2.5, by = 0.5)) +
  theme_bw() +
  geom_vline(xintercept = 0.5, linetype = "dashed", alpha = 0.6) +
    labs(
      title = "1000 Confidence Intervals of the mycifun() Function",
      y = NULL,
      color = "Contains True Beta1 = 0.5",
      caption = glue("Proportion Containing True Beta1 = {sum(ci_dat$cover)/length(ci_dat$cover)}")
    )

```

-   At least one numeric variable and one categorical variable **Lab 7 Question 3**

```{r}
#| label: dvs-2-num-cat
#Feedback: I would still recommend recoding the trip variable before plotting, so the facets have more informative names like "Trip 1" instead of "1". You have a variety of tools you’ve learned that would be a good fit for this task -- if_else() or fct_recode() would be great places to start!

#How could you use yout plot title to convey additional information regarding the context of these data?

mycolors <- RColorBrewer::brewer.pal(12, "Paired")[c(7,12)] # color palette

fishdata |> 
  mutate(
    trip = as.factor(if_else(trip == 1,"Trip 1", "Trip 2")),
    year = as.factor(year)) |> 
  group_by(trip, year, section) |> 
    summarize(
      n_NA = sum(is.na(weight)),
      .groups = "drop") |> 
ggplot(mapping = aes(x = year, y = n_NA, fill = section)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = n_NA), 
            position = position_dodge(width = 0.9),
            vjust = -0.5, 
            size = 3) +
  facet_wrap(~trip, ) +
  theme_bw() + 
  theme(
    plot.title = element_text(face = "bold", size = 13)) +
  scale_fill_manual(values = mycolors,
                     labels = c("Jonsrud",
                                "Scotty Brown")) +
  labs(
    title = "Missing Data Between Survey Trips 1989-1991",
    subtitle = "from Blackfoot River, Helena, Montana",
    x = "Year",
    y = "Number of Missing Values",
   fill = "River Section")
```

-   At least two categorical variables **Challenge 3 Question 2**

```{r}
#| label: dvs-2-cat

ggplot(data = teacher_evals_compare, 
      mapping = aes(x = sen_level, fill = SET_level)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = label_percent()) +
  scale_fill_manual(
    values = c(
       "excellent" = "#B297D0",
       "standard" = "#B49664")) +
  theme_bw() +
  theme(legend.position = "top") +
  labs(title= "Evalutation of Teachers' Use of Activities",
      x = "Years of Experience",
      y = NULL,
      fill = "Evaluation Rating")
```

-   Dates (time series plot) **Challenge 7 Question 5**

```{r}
#| label: dvs-2-date

mycolors <- RColorBrewer::brewer.pal(12, "Paired")[c(7,12,8,2)] # color palette

fishdata |> 
  mutate(
    condition_index = condition(weight,length),
    species = as.factor(species)) |> 
  group_by(year, species) |> 
  summarize(
    mean_condition = mean(condition_index, na.rm = TRUE),
    .groups = "drop") |>
  mutate(
    species = fct_reorder2(.f = species, .x =year, .y = mean_condition, .desc = TRUE)) |> 
ggplot(mapping = aes(x = year, y = mean_condition, color = species)) +
  geom_rug(sides = "b", color = "#ffdbec", length = unit(100, "npc")) +
  geom_smooth(se = FALSE) +
  geom_point() +
  theme_bw() + 
  scale_color_manual(values = mycolors,
                     labels = c("Rainbow Trout",
                                "Brown Trout",
                                "Westslope Cutthroat Trout",
                                "Bull Trout")) +
  scale_x_continuous(
             breaks = seq(1989, 2006, by = 2)) + # only show every 2 years
  labs(
    title = "Condition Indices of Trout Over Time",
    subtitle = "Mean Condition Index",
    x = "Year",
    y = NULL,
    color = "Trout Species")
```

**DVS-2: I use plot modifications to make my visualization clear to the reader.**

-   I can modify my plot theme to be more readable **Lab 7 Question 3**

```{r}
#| label: dvs-2-ex-1
#Feedback: I would still recommend recoding the trip variable before plotting, so the facets have more informative names like "Trip 1" instead of "1". You have a variety of tools you’ve learned that would be a good fit for this task -- if_else() or fct_recode() would be great places to start!

#How could you use yout plot title to convey additional information regarding the context of these data?

mycolors <- RColorBrewer::brewer.pal(12, "Paired")[c(7,12)] # color palette

fishdata |> 
  mutate(
    trip = as.factor(if_else(trip == 1,"Trip 1", "Trip 2")),
    year = as.factor(year)) |> 
  group_by(trip, year, section) |> 
    summarize(
      n_NA = sum(is.na(weight)),
      .groups = "drop") |> 
ggplot(mapping = aes(x = year, y = n_NA, fill = section)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = n_NA), 
            position = position_dodge(width = 0.9),
            vjust = -0.5, 
            size = 3) +
  facet_wrap(~trip, ) +
  theme_bw() + 
  theme(
    plot.title = element_text(face = "bold", size = 13)) +
  scale_fill_manual(values = mycolors,
                     labels = c("Jonsrud",
                                "Scotty Brown")) +
  labs(
    title = "Missing Data Between Survey Trips 1989-1991",
    subtitle = "from Blackfoot River, Helena, Montana",
    x = "Year",
    y = "Number of Missing Values",
   fill = "River Section")
```

-   I can modify my colors to be accessible to anyone's eyes **Lab 4 Question 7**

```{r}
#| label: dvs-2-ex-2

mycolors<- colorRampPalette(brewer.pal(7, "Paired"))(10) #The Paired palette is color-deficiency friendly!
  
ggplot(data = recreate_plot, 
        mapping = aes(x = study_year, y = price, color = census_region)) +
        geom_point(size = 0.75) +
        geom_smooth(linewidth = 0.75) +
        facet_wrap(~factor(age, c("Infant", "Toddler", "Preschool"))) +
         scale_y_continuous(labels = label_currency(prefix = "$")) +
         scale_x_continuous(
             breaks = seq(2008, 2018, by = 2),  # only show every 2 years
             limits = c(2008, 2018)) +
        theme_bw(base_size = 10) +
        labs(
          title = "Weekly Median Price for Center-Based Childcare ($)",
           x = "Study Year",
           y = NULL,
           color = "California Region") +
  scale_color_manual(values = mycolors)
```

-   I can modify my plot titles to clearly communicate the data context **Challenge 4 Plot of the Data**

```{r}
#| label: dvs-2-ex-3

ggplot(data = my_research_long, 
        mapping = aes(x = study_year, y = price, color = care_type)) +
        geom_point() +
        geom_smooth(linewidth = 0.75) +
        facet_wrap(~census_region, scales = "free", ncol = 3) +
        scale_y_continuous(labels = label_currency(prefix = "$")) +
        scale_x_continuous(
             breaks = seq(2008, 2018, by = 2)) + # only show every 2 years
       theme_bw(base_size = 12) +
        theme(aspect.ratio = 1.25) +
        labs(
          title = "Weekly Median Price for Toddler Childcare for Regions in California ($)",
           x = "Study Year",
           y = NULL,
           color = "Type of Care")
```

-   I can modify the text in my plot to be more readable **Lab 10 Question 3 - Revised**

```{r}
#| label: dvs-2-ex-4
#Feedback: What are the sample sizes of these simulations? That information should be included in the plot title!

# change y axis labels to percentages and add the exact percentages on top of the bars

results |> 
enframe() |> 
  count(value) |> 
  mutate(
    n = n/sum(n),
    value = as.factor(value)
  ) |> 
ggplot(mapping = aes(x = value, y = n, fill = value)) +
  geom_col(color = "black",
           linewidth = 0.1 ) +
  geom_text(aes(label = sprintf("%.1f%%", n * 100)), 
            position = position_dodge(width = 0.9),
            vjust = -0.5, 
            size = 3) +
  scale_y_continuous(limits = c(0, 0.40),
                     breaks = seq(0, .40, by = 0.1),
                     labels = label_percent()) +
  theme_bw() + 
  theme(
    plot.title = element_text(face = "bold", size = 13),
    legend.position = "none") +
  labs(
    title = "How Often Babies are Correctly Paired at the Nightmare Hospital",
    subtitle = "Percent Correct of 10,000 Simulations of 4 Babies Born a Night",
    x = "# of Correct Pairs",
    y = NULL,
    fill = NULL) +
  scale_fill_manual(
    values = c(
      "0" = "#cfecfc",  
      "1" = "#fccfeb",  
      "2" = "#e6cffc",
      "4" = "#c9f5ce" 
    )
  )
```

-   I can reorder my legend to align with the colors in my plot **Lab 4 Question 7**

```{r}
#| label: dvs-2-ex-5

#reorder legend using fct_reorder and then plotting with ggplot

recreate_plot <- ca_childcare |> 
  select(county_name, 
         study_year, 
         mc_infant, 
         mc_toddler, 
         mc_preschool, 
         census_region) |>
  pivot_longer(cols = mc_infant:mc_preschool,
             names_to = "age",
             values_to = "price") |> 
  mutate(age = case_when(age == "mc_infant" ~ "Infant",
                         age == "mc_toddler" ~ "Toddler",
                         age == "mc_preschool" ~ "Preschool",
                         TRUE ~ age),
    census_region = fct_reorder2(.f = census_region, .x = study_year, #using factor reorder for legend order
                 .y = price, 
                .desc = TRUE))
library(RColorBrewer)

mycolors<- colorRampPalette(brewer.pal(7, "Accent"))(10) #take color palette that has only 7 colors into 10
  
ggplot(data = recreate_plot, 
        mapping = aes(x = study_year, y = price, color = census_region)) + #this will be ordered now
        geom_point(size = 0.75) +
        geom_smooth(linewidth = 0.75) +
        facet_wrap(~factor(age, c("Infant", "Toddler", "Preschool"))) +
         scale_y_continuous(labels = scales::dollar_format(
                                prefix = "$", big.mark = ",")) +
         scale_x_continuous(
             breaks = seq(2008, 2018, by = 2),  # only show every 2 years
             limits = c(2008, 2018)) +
        theme_bw(base_size = 10) +
        theme(aspect.ratio = 1.25) +
        labs(
          title = "Weekly Median Price for Center-Based Childcare ($)",
           x = "Study Year",
           y = NULL,
           color = "California Region") +
  scale_color_manual(values = mycolors)
```

**DVS-3: I show creativity in my visualizations**

-   I can use non-standard colors (Example 1) **Challenge 2 Spicy**

```{r}
#| label: dvs-3-1-ex-1

ggplot(data = surveys, 
        mapping = aes(x = species, y = weight)) +
        geom_jitter(width = 0.2, 
                    height = 0, 
                    alpha = 0.2, 
                    color = "darkseagreen")+
       geom_boxplot(alpha = 0, 
                  color = "darkgreen",
                  outliers = FALSE,
                  median.color= "black",
                  median.linewidth = 0.75, 
                  box.linewidth= 0.25) +
        theme_bw(base_size = 12, base_family = "times new roman") +
   theme(axis.text.x = element_text(angle = 30),
         panel.border = element_rect(colour = "darkgreen", linewidth=2)) +
        labs(
          title = "Comparing Median Weight between Rodent Species",
           x = "Species",
          y = "Weight" 
        )
```

-   I can use non-standard colors (Example 2) - **Challenge 4 Plot of the Data**

```{r}
#| label: dvs-3-1-ex-2

mycoolcolors =colorRampPalette(brewer.pal(7, "Accent"))(10)

ggplot(data = my_research_long, 
        mapping = aes(x = study_year, y = price, color = care_type)) +
        geom_point() +
        geom_smooth(linewidth = 0.75) +
        facet_wrap(~census_region, scales = "free", ncol = 3) +
        scale_y_continuous(labels = scales::dollar_format(prefix = "$", big.mark = ",")) +
        scale_x_continuous(
             breaks = seq(2008, 2018, by = 2)) + # only show every 2 years
        theme_bw(base_size = 12) +
        theme(aspect.ratio = 1.25, axis.text.x = element_text(angle = 30)) +
        labs(
          title = "Weekly Median Price for Toddler Childcare for Regions in California ($)",
           x = "Study Year",
           y = NULL,
           color = "Type of Care") +
      scale_color_manual(values = mycoolcolors)
        
```

-   I can use annotations (e.g., `geom_text()`)

```{r}
#| label: dvs-3-2

results |> 
enframe() |> 
  count(value) |> 
  mutate(
    n = n/sum(n),
    value = as.factor(value)
  ) |> 
ggplot(mapping = aes(x = value, y = n, fill = value)) +
  geom_col(color = "black",
           linewidth = 0.1 ) +
  geom_text(aes(label = sprintf("%.1f%%", n * 100)), 
            position = position_dodge(width = 0.9),
            vjust = -0.5, 
            size = 3) +
  scale_y_continuous(limits = c(0, 0.40),
                     breaks = seq(0, .40, by = 0.1),
                     labels = label_percent()) +
  theme_bw() + 
  theme(
    plot.title = element_text(face = "bold", size = 13),
    legend.position = "none") +
  labs(
    title = "How Often Babies are Correctly Paired at the Nightmare Hospital",
    subtitle = "Percent Correct",
    x = "# of Correct Pairs",
    y = NULL,
    fill = NULL) +
  scale_fill_manual(
    values = c(
      "0" = "#cfecfc",  
      "1" = "#fccfeb",  
      "2" = "#e6cffc",
      "4" = "#c9f5ce" 
    )
  )
```

-   I can choose creative geometries (e.g., `geom_segment()`, `geom_ribbon)()`)

```{r}
#| label: dvs-3-3

ci_dat |> 
  arrange(estimate) |> 
  mutate(
    cover = as.factor(cover)
  ) |> 
  ggplot(mapping = aes(y = c(1:1000), xmin = conf.low, xmax = conf.high, color = cover)) +
  geom_errorbar() + 
  scale_color_manual(values = RColorBrewer::brewer.pal(9, "Set1")[c(1,2)],
                     labels = c("No",
                                "Yes")) +
  scale_y_continuous(labels = NULL) +
  scale_x_continuous(
             breaks = seq(-2.5, 2.5, by = 0.5)) +
  theme_bw() +
  geom_vline(xintercept = 0.5, linetype = "dashed", alpha = 0.6) +
    labs(
      title = "1000 Confidence Intervals of the mycifun() Function",
      y = NULL,
      color = "Contains True Beta1 = 0.5",
      caption = glue("Proportion Containing True Beta1 = {sum(ci_dat$cover)/length(ci_dat$cover)}")
    )
```

**DVS-4: I can calculate numerical summaries of variables.**

-   Example using `summarize()` **Lab 3 Question 6**

```{r}
#| label: dvs-4-summarize
#Feedback: Could your output be more concise? Could your output be only the information necessary to answer the question?
#Can you get both of these summary statistics in **one** pipeline? You will want to use the summarize() function!

teacher_evals_clean |>
  summarize(
    courses = n_distinct(course_id),
    teachers = n_distinct(teacher_id)
  )
```

-   Example using `across()` - **Lab 7 Question 1**

```{r}
#| label: dvs-4-across

fishdata |> 
  summarize(
    across(
      .cols = everything(),
      .fns = ~ sum(is.na(.x))
  ))
```

**DVS-5: I can find summaries of variables across multiple groups.**

-   Example 1 **Lab 3 Question 12**

```{r}
#| label: dvs-5-1

#Feedback: I would recommend using the %in% operator instead of the or! Look at your output! You have the same row repeated 6 times! Is there a way to get only one row with this information?

teacher_evals_clean |> 
  filter(academic_degree %in% c("dr","prof"))|>
  group_by(teacher_id, sex, seniority) |>
  summarize(
    avg_percent_resp = mean(resp_share, na.rm = TRUE),
    .groups = "drop")|> 
      filter(avg_percent_resp %in% c(min(avg_percent_resp),max(avg_percent_resp))) |> 
  arrange(desc(avg_percent_resp))
```

-   Example 2 **Lab 4 Question 5**

```{r}
#| label: dvs-5-2

median_inc_change <- ca_childcare |> 
  select(county_name, 
         study_year, 
         census_region, 
         mhi_2018) |> 
  filter(study_year %in% c(2008,2018)) |> 
  pivot_wider (names_from = study_year,
               values_from = mhi_2018) |> 
  group_by(census_region) |> 
  summarize(
    median_inc_2018 = median(`2018`),
    median_inc_2008 = median(`2008`),
    .groups = "drop" ) |> 
  arrange(desc(median_inc_2018))
```

**DVS-6: I can create tables which make my summaries clear to the reader.**

-   I can modify my column names to clearly communicate the data context **Lab 9 Question 2**

```{r}
#| label: dvs-6-ex-1
#| 
surveys |> 
  map_chr(.f = ~ class(.x)) |> 
  enframe() |> 
  mutate(
    name = str_to_title(str_replace_all(name, 
                pattern = "_", 
                replacement = " ")),
    value = str_to_title(value)) |> 
  kable(
  col.names = c("Variable", "Data Type"),
  align = 'c',
  caption = "Data Types in the Surveys Dataset") |> 
  kable_classic(full_width = F, html_font = "Cambria")
```

-   I can modify the text in my table to be more readable (e.g., bold face for column headers) **Lab 9 Question 3**

```{r}
#| label: dvs-6-ex-2

surveys |> 
  map_chr(.f = ~ class(.x)) |> 
  enframe() |> 
  arrange(value) |> 
  mutate(
    name = str_to_title(str_replace_all(name,  
                pattern = "_", 
                replacement = " ")),
    value = str_to_title(value)) |> 
  kable(
  col.names = c("Variable", "Data Type"),
  align = 'c',
  caption = "Data Types in the Surveys Dataset") |> 
  kable_styling(full_width = FALSE,
                bootstrap_options = "striped")
```

-   I can arrange my table to have an intuitive ordering **Lab 9 Question 6**

```{r}
#| label: dvs-6-ex-3
#table is ordered by groups

evals_table |>
  gt(groupname_col = "variable") |> 
  tab_header(
    title = "Instructor Demographics",
    subtitle = "From Student Evaluations at the University of Poland, Warsaw in 2020"
  ) |>
  fmt_percent(
    columns = prop,
    decimals = 2
  ) |> 
    cols_label(
    level = md("**Demographic**"),
    n = md("**Count**"),
    prop = md("**%**")) |> 
  tab_spanner(
    label = "Professors",
    columns = c(n, prop))|> 
  tab_style(
    style = cell_fill(color = "#cce3af"),
    locations = list(cells_row_groups(everything()), cells_title(groups = "title"))) |> 
   tab_style(
    style = cell_borders(
      sides = c("t", "b", "l", "r"),
      color = "black",
      weight = px(2)),
    locations = list(cells_column_labels(), cells_stubhead(), cells_title(), cells_body(), cells_row_groups(), cells_column_spanners())
  ) |> 
  tab_style(
    style = cell_text(font = system_fonts(name = "classical-humanist")),
    locations = list(cells_body(), cells_column_labels(), cells_title(), cells_row_groups())
  )
```

**DVS-7: I show creativity in my tables.**

-   I can use non-default colors **Lab 9 Question 8**

```{r}
#| label: dvs-7-ex-1

fish |> 
  map_int(.f = ~ sum(is.na(.x))) |> 
  enframe() |> 
  mutate(
    name = str_to_title(name)
  ) |> 
  arrange(value, name) |> 
  gt() |> 
  data_color(
    method = "numeric",
    palette = RColorBrewer::brewer.pal(3, "Set1")[c(3,1)]) |> 
  tab_header(
    title = md("**Missing Values for Fish Measurements**"),
    subtitle = "1989-2006 - Blackfoot Fish River in Montana"
  ) |> 
  cols_label(
    name = md("**Variable**"),
    value = md("**Number Missing**")
  ) |> 
  tab_style(
    style = cell_borders(
      sides = c("t", "b", "l", "r"),
      color = "black",
      weight = px(2)),
    locations = list(cells_column_labels(), cells_stubhead(), cells_title(), cells_body())
  ) |> 
  tab_style(
    style = cell_text(font = system_fonts(name = "classical-humanist")),
    locations = list(cells_body(), cells_column_labels(), cells_title())
  )
```

-   I can modify the layout of my table to be more readable (e.g., `pivot_longer()` or `pivot_wider()`) **Lab 9 Question 5**

```{r}
#| label: dvs-7-ex-2

evals_table <- evals |> 
  distinct(teacher_id, academic_degree, seniority, sex) |> 
  mutate(
   seniority = case_when(seniority <= 4 ~ "junior", 
                    .default = "senior")) |> 
  pivot_longer(
    c(academic_degree, seniority, sex),
    names_to  = "variable",
    values_to = "level"
  ) |> 
  mutate(
    variable = str_to_title(str_replace(variable,
                                        pattern = "_",
                                        replacement = " ")),
    level = case_when(level == "no_dgr" ~ "No Degree",
                      level == "ma" ~ "Masters",
                      level == "dr" ~ "Doctorate",
                      level == "prof" ~ "Tenured Professor",
                      .default = level),
    level = str_to_title(level)) |> 
  count(variable, level, name = "n") |> 
  group_by(variable) |> 
  mutate(
    prop = n/sum(n)) |> 
  ungroup()
  
```

## Program Efficiency

**PE-1: I can write concise code which does not repeat itself.**

-   using a single function call with multiple inputs (rather than multiple function calls) **Lab 5 Identify Murderer**

```{r}
#| label: pe-1-one-call

detective |> 
  filter(hair_color == "red", 
         gender == "female", 
         car_make == "Tesla", 
         car_model == "Model S", 
         between(height, 65, 67), 
         event_name == "SQL Symphony Concert") |> 
  summarize(name)

```

-   using `across()` - **Lab 3 Question 8**

```{r}
#| label: pe-1-across

teacher_evals_clean |>
  filter(if_any( #if any is an across
    .cols = everything(), 
    .fns = ~ is.na(.x)))
```

-   using functions from the `map()` family **Lab 9 Question 4**

```{r}
#| label: pe-1-map-1

evals <- evals |> 
  map_if(.x = evals,
         .p = is.character,
         .f = ~ as.factor(.x)) |> 
  bind_cols()
```

**PE-2: I can write functions to reduce repetition in my code.**

-   Example 1: Function that operates on vectors - **Challenge 7 Question 2**

```{r}
#| label: pe-2-1
# Feedback: t looks like you are checking multiple condtions in your if_else() function. This is exactly what the case_when() function is built for!

#Where are your function checks? What types of inputs does your function expect?
  
restrict <- function(x, min, max) {
  stopifnot("Input 'x' must be a numeric value." = is.numeric(x))
  if (length(x) < 1) stop("Input vector must have length >= 1!")
  
  case_when(x < min ~ NA,
            x > max ~ NA,
            .default = x)
}
```

-   Example 2: Function that operates on data frames **Lab 8 Question 1**

```{r}
#| label: pe-2-2
# Sucess Feedback: Nice use of the modern syntax for across()!

rescale_column <- function(df, cols){
  df |> 
   mutate(
       across(.cols = {{cols}},
              .fns = ~ rescale_01(.x)
              )
       )
}
```

-   Example 3: Function that operates on vectors *or* data frames **Lab 7 Question 4**

```{r}
#| label: pe-2-3

rescale_01 <- function(x){
  stopifnot(is.numeric(x))
  if (length(x) < 1) stop("Input vector must have length >= 1!")
  rng <- range(x, na.rm = TRUE)
  x = (x - rng[1]) / (rng[2] - rng[1])
}
```

**PE-3: I can use iteration to reduce repetition in my code.**

-   using `across()` **Lab 8 Question 1**

```{r}
#| label: pe-3-across


rescale_column <- function(df, cols){
  df |> 
   mutate(
       across(.cols = {{cols}},
              .fns = ~ rescale_01(.x)
              )
       )
}
```

-   using a `map()` function with **one** input (e.g., `map()`, `map_chr()`, `map_dbl()`, etc.) **Lab 9 Question 2**

```{r}
#| label: pe-3-map-1

surveys |> 
  map_chr(.f = ~ class(.x)) |> 
  enframe() |> 
  mutate(
    name = str_to_title(str_replace_all(name, 
                pattern = "_", 
                replacement = " ")),
    value = str_to_title(value)) |> 

  kable(
  col.names = c("Variable", "Data Type"),
  align = 'c',
  caption = "Data Types in the Surveys Dataset") |> 
  kable_classic(full_width = F, html_font = "Cambria")
```

-   using a `map()` function with one input **Lab 9 Question 4**

```{r}
#| label: pe-3-map-2

evals <- evals |> 
  map_if(.x = evals,
         .p = is.character,
         .f = ~ as.factor(.x)) |> 
  bind_cols()

```

**PE-4: I can use modern tools when carrying out my analysis.**

-   I can use functions which are not superseded or deprecated **Lab 4 Question 7**

```{r}
#| label: pe-4-1

#label_currency is a modern function that was the new verson of dollar_format

ggplot(data = recreate_plot, 
        mapping = aes(x = study_year, y = price, color = census_region)) +
        geom_point(size = 0.75) +
        geom_smooth(linewidth = 0.75) +
        facet_wrap(~factor(age, c("Infant", "Toddler", "Preschool"))) +
         scale_y_continuous(labels = label_currency(prefix = "$")) + #modern label function
         scale_x_continuous(
             breaks = seq(2008, 2018, by = 2),  # only show every 2 years
             limits = c(2008, 2018)) +
        theme_bw(base_size = 10) +
        labs(
          title = "Weekly Median Price for Center-Based Childcare ($)",
           x = "Study Year",
           y = NULL,
           color = "California Region") +
  scale_color_manual(values = mycolors)
```

-   I can connect a data wrangling pipeline into a `ggplot()` **Lab 7 Question 3**

```{r}
#| label: pe-4-2
#Feedback: I would still recommend recoding the trip variable before plotting, so the facets have more informative names like "Trip 1" instead of "1". You have a variety of tools you’ve learned that would be a good fit for this task -- if_else() or fct_recode() would be great places to start!

#How could you use yout plot title to convey additional information regarding the context of these data?

#also using the native pipe operator (modern tool)

mycolors <- RColorBrewer::brewer.pal(12, "Paired")[c(7,12)] # color palette

fishdata |> 
  mutate(
    trip = as.factor(if_else(trip == 1,"Trip 1", "Trip 2")),
    year = as.factor(year)) |> 
  group_by(trip, year, section) |> 
    summarize(
      n_NA = sum(is.na(weight)),
      .groups = "drop") |> 
ggplot(mapping = aes(x = year, y = n_NA, fill = section)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = n_NA), 
            position = position_dodge(width = 0.9),
            vjust = -0.5, 
            size = 3) +
  facet_wrap(~trip, ) +
  theme_bw() + 
  theme(
    plot.title = element_text(face = "bold", size = 13)) +
  scale_fill_manual(values = mycolors,
                     labels = c("Jonsrud",
                                "Scotty Brown")) +
  labs(
    title = "Missing Data Between Survey Trips 1989-1991",
    subtitle = "from Blackfoot River, Helena, Montana",
    x = "Year",
    y = "Number of Missing Values",
   fill = "River Section")
```

## Data Simulation & Statistical Models

**DSSM-1: I can simulate data from a *variety* of probability models.**

-   Example 1 **Lab 10 Question 1**

```{r}
#| label: dsm-1-1

randomBabies <- function(n_babies){
  
  baby <- tibble(correct_parent = 1:n_babies,
                 new_parent = sample(1:n_babies,
                                     size = n_babies,
                                     replace = FALSE))
  correct_pairs <- baby |>
    filter(correct_parent == new_parent) |> 
    nrow()
  
  correct_pairs
  
}
```

-   Example 2 **Lab 10 Question 4**

```{r}
#| label: dsm-1-2

set.seed(525600)

# define slope and intercept parameters
intercept = 2
slope = 1

# generate x vector
x = runif(n = 100,
      min= 0,
      max = 1)

# generate noise `ep` vector
ep = rnorm(n = 100,
      mean = 0,
      sd = 1)

# generate outcome from population model
y = intercept + x*slope + ep


# create an "observed data" dataframe with only the x and y vectors
obs_data <- tibble(y,
                   x)
```

**DSSM-2: I can conduct common statistical analyses in R.**

-   Example 1 **Lab 10 Question 7**

```{r}
#| label: dsm-2-1

mod <- lm(y ~ x, data = obs_data)
```

-   Example 2 **Lab 3 Question 3**

```{r}
#| label: dsm-2-2

chisq.test(teacher_evals_compare$SET_level,
           teacher_evals_compare$sen_level)
```

-   Example 3 **Lab 2 Question 17**

```{r}
#| label: dsm-2-3

aov(weight ~ species, data = surveys)
```

## Revising My Thinking

I quickly realized after receiving feedback on the first few assignments that there are often more efficient ways to perform tasks than my first idea. It took effort to learn new functions and troubleshoot, but throughout the course I have worked hard to recognize the errors in my own thinking and revise them. I often started from "square 1," brainstorming all the different ways to approach a problem and implementing the most efficient one. I used feedback from every assignment to submit thoughtful revisions for my growing areas, and I did my best to implement what I learned from revisions into my future work. In my portfolio, I revised earlier assignments based not only on feedback from back then, but the skills I have acquired now. For example, DEVS-2 example 2 uses my recent understanding of unique color palettes applied to a graph from earlier in the course.

## Extending My Thinking

I have learned to love Stack Overflow and reading code documentation to implement creative solutions and visualizations into my code. In addition to the resources in the course materials, I constantly used outside research to supplement the tools I was using. I feel that all of my Lab 10: Simulation Exploration work showed my desire to extend my understanding of the functions that we were only required to be using at their basic level. This hard work comes from the fact that the career I want is reliant on these data manipulation skills, so I have made the extra effort to truly understand their complexities.

## Peer Support & Collaboration

**Feedback Example:**

**"First of all, I love the theme of your output! The white font is a little small and hard to read on the background but still super cute!"**

I am proud of this feedback where I praised a student for customozing their Quarto theme. I think it is extremely important to lift people up for going the extra mile creatively. As a creative person, I feel that it is sometimes difficult in this area of study to find expressive outlets in assignments, so I wanted the student to know that their extra effort was impactful.

**Feedback Example:**

**"Make sure when you load in your data and libraries that you put {r, message=FALSE} in each code chunk to silence the messages. It took me forever to figure out where to put it, but it helps with readability!"**

I am also proud of my feedback when I gave a student a tip about silencing messages because I let them know that I was also struggling alongside them, which always makes me feel better when I receive a peer review. These reviews are about building off of each others skills, helping each other stay consistent, and sharing knowledge rather than comparing yourself to your classmates.

In addition to these specific examples, I consistently gave my peers feedback on code tidiness and efficiency, letting them know where they were missing spaces, indentation, or named arguments.

I initially struggled in the "computer" role during collaboration because I wanted to answer the problem as soon as I knew the method to do it. However, I understood that it was important to honor the learning experience for my partner in the "coder" role. I thought of how I would want to be challenged if I was the "coder." I asked questions that lead them to think about the pathway to the solution, rather than just giving the answer myself. Having mutual respect for the learning process of another student allowed me to grow as a collaborator and coder when I was in that role. I think I did a good job communicating with other students and often made new friends!

## Grade Reasoning

I believe that I deserve an A on this portfolio because I have displayed my skills to achieve the learning target in each code chunk. I have also updated code chunks with feedback from past assignments to include shortcuts and modern tools that I would not have known at that time such as the %in% operator. I take extra time to show my creativity, ask questions to better my understanding, and effectively implement new skills as I learn them. For these reasons, I believe that an A is the proper grade for this midterm portfolio, recognizing that although my code is not perfect every time, I am an efficient, tidy, and creative coder who makes an extra effort to revise my assignments, push my limits, and learn through collaboration.
